### 2025-06-09 mixed-models.qmd
20250609 - tweak

```{r}
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("bbmle")
library("rstan")
library("brms")
library("cmdstanr") # todo: install.packages("cmdstanr", repos = c("https://stan-dev.r-universe.dev", getOption("repos"))); check_cmdstan_toolchain(); cmdstanr::install_cmdstan()
library("fitdistrplus")
library("performance")
library("parallel")
library("parallelly")
library("plotly")
library("viridis")
library("tidyverse")
```

>>>>

```{r}
library("lme4")
library("lmerTest")
library("MuMIn")
library("emmeans")
library("sjstats")
library("mgcv")
library("AICcmodavg")
library("bbmle")
library("rstan")
library("brms")
library("cmdstanr") # todo: install.packages("cmdstanr", repos = c("https://stan-dev.r-universe.dev", getOption("repos"))); cmdstanr::check_cmdstan_toolchain(); cmdstanr::install_cmdstan()
library("fitdistrplus")
library("performance")
library("parallel")
library("parallelly")
library("plotly")
library("viridis")
library("tidyverse")
```
